EDLD 651 Final Project Presentation

### 2020-11-30 presentation.Rmd
a few last minute changes
added extra figure and final gif

###
<small> Dwell times ***increase*** as complexity ***increases*** during the ***growth*** phase.
</small>

@@

<!-- <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/00scott.png" height="360" width="480"> -->

@@

## Thank you slide

>>>>

<small> Dwell times ***increase*** as complexity ***increases*** during the ***growth*** phase.
</small>

@@

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/0007.png" height="480" width="640">

##
<small> Dwell times ***increase*** as complexity ***increases*** during the ***growth*** phase.
</small>

@@

##
We all admit, that we had a blast with this project.

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/83QZ.gif" height="400" width="800">
